4-5-interactive

### 2022-04-17 2-the-cubble-pkg.Rmd
%>% to |>

```{r echo = TRUE}
cubble_nested <- cubble::climate_flat %>%
  as_cubble(key = id, index = date, coords = c(long, lat))
cubble_nested
```

@@

```{r echo = TRUE}
cubble_long <- cubble_nested %>% face_temporal()
cubble_long
```

@@

```{r echo = TRUE}
cubble_back <- cubble_long %>% face_spatial()
cubble_back
```

@@

```{r echo = TRUE}
cubble_mig <- cubble_long %>% unfold(long, lat)
cubble_mig
```

@@

```{r echo = TRUE}
cubble_mig %>% face_spatial() %>% face_temporal()
```

@@

<!-- ```{r eval = FALSE} -->
<!-- library(cubble) -->
<!-- library(tidyverse) -->
<!-- left_join(cubble::stations, cubble::climate) %>%  -->
<!--   dplyr::nest_by(id, lat,  long,  elev, name, wmo_id) %>%  -->
<!--   tidyr::unnest() %>%  -->
<!--   group_by(........, geometry) -->
<!-- ``` -->

@@

```{r echo = TRUE}
# example with a tsibble created from climate_flat
raw <- climate_flat %>%
  tsibble::as_tsibble(key = id, index = date)

dt <-  raw %>%
  cubble::as_cubble(coords = c(long, lat))
dt
```

@@

```{r echo = TRUE}
# add station-based features in the nested form.
dt %>%
  mutate(fabletools::features(ts, tmax, list(tmax_mean = mean, tmax_var = var)))
```

@@

```{r echo = TRUE}
library(sf)
# create a cubble
cb <- climate_flat %>%
  cubble::as_cubble(key = id, index = date, coords = c(long, lat))

@@

dt <- cb %>%
  mutate(
    # create `sfc` column based on long and lat
    ll = st_sfc(
      purrr::map2(long, lat, ~st_point(c(.x, .y))),
      crs = st_crs(aus)),

@@

```{r echo = TRUE}
library(s2)
# Western Australia map
wa <- ozmaps::abs_ste %>% filter(NAME == "Western Australia")

# mutate a `s2_lnglat` vector on `cb` created in the last chunk
cb %>%
  mutate(ll = s2_lnglat(long, lat)) %>%
  filter(s2_within(ll, wa))
```

>>>>

```{r echo = TRUE}
cubble_nested <- cubble::climate_flat |>
  as_cubble(key = id, index = date, coords = c(long, lat))
cubble_nested
```

@@

```{r echo = TRUE}
cubble_long <- cubble_nested |> face_temporal()
cubble_long
```

@@

```{r echo = TRUE}
cubble_back <- cubble_long |> face_spatial()
cubble_back
```

@@

```{r echo = TRUE}
cubble_mig <- cubble_long |> unfold(long, lat)
cubble_mig
```

@@

```{r echo = TRUE}
cubble_mig |> face_spatial() |> face_temporal()
```

@@

<!-- ```{r eval = FALSE} -->
<!-- library(cubble) -->
<!-- library(tidyverse) -->
<!-- left_join(cubble::stations, cubble::climate) |>  -->
<!--   dplyr::nest_by(id, lat,  long,  elev, name, wmo_id) |>  -->
<!--   tidyr::unnest() |>  -->
<!--   group_by(........, geometry) -->
<!-- ``` -->

@@

```{r echo = TRUE}
# example with a tsibble created from climate_flat
raw <- climate_flat |>
  tsibble::as_tsibble(key = id, index = date)

dt <-  raw |>
  cubble::as_cubble(coords = c(long, lat))
dt
```

@@

```{r echo = TRUE}
# add station-based features in the nested form.
dt |>
  mutate(fabletools::features(ts, tmax, list(tmax_mean = mean, tmax_var = var)))
```

@@

```{r echo = TRUE}
library(sf)
# create a cubble
cb <- climate_flat |>
  cubble::as_cubble(key = id, index = date, coords = c(long, lat))

@@

dt <- cb |>
  mutate(
    # create `sfc` column based on long and lat
    ll = st_sfc(
      purrr::map2(long, lat, ~st_point(c(.x, .y))),
      crs = st_crs(aus)),

@@

```{r echo = TRUE}
library(s2)
# Western Australia map
wa <- ozmaps::abs_ste |> filter(NAME == "Western Australia")

# mutate a `s2_lnglat` vector on `cb` created in the last chunk
cb |>
  mutate(ll = s2_lnglat(long, lat)) |>
  filter(s2_within(ll, wa))
```

### 2022-04-17 3-advanced.Rmd
%>% to |>

```{r illu-matching, out.width="100%", fig.cap="An illustration of temporal matching in cubble. Three highest peaks are identified in each series and intervals are constructed on series \\code{A}. Two peaks in series \\code{a} fall into the intervals and hence the two series are considered to have 2 matches."}
knitr::include_graphics("figures/illu-matching.png")
```

>>>>

```{r illu-matching, out.width="100%", fig.cap="An illustration of temporal matching in cubble. Three highest peaks are identified in each series and intervals are constructed on series \\code{A}. Two peaks in series \\code{a} fall into the intervals and hence the two series are considered to have 2 matches."}
knitr::include_graphics(here::here("figures/illu-matching.png"))
```

### 2022-04-17 4-1-basic.Rmd
%>% to |>

```{r eval = FALSE, echo = TRUE}
tmax <- weatherdata::historical_tmax %>%
  filter(between(stringr::str_sub(id, 7, 8), 46, 90))
```

@@

```{r eval=  FALSE, echo = TRUE}
tmax <- tmax %>% 
  face_temporal() %>%
  filter(lubridate::year(date) %in% c(1971:1975, 2016:2020)) 
```

@@

```{r eval=  FALSE, echo = TRUE}
tmax <- tmax %>%
  group_by(month = lubridate::month(date), 
         group = as.factor(ifelse(lubridate::year(date) > 2015, 
                                  "2016 ~ 2020", "1971 ~ 1975"))) %>%
  summarise(tmax = mean(tmax, na.rm = TRUE))
```

@@

```{r eval = FALSE, echo = TRUE}
tmax <- tmax %>% face_spatial() %>% filter(nrow(ts) == 24) 
```

@@

```{r eval = FALSE, echo = TRUE}  
tmax <- tmax %>% face_temporal() %>% unfold(latitude, longitude)
```

@@

```{r eval = FALSE, echo = TRUE}
nsw_vic <- ozmaps::abs_ste %>% 
  filter(NAME %in% c("Victoria", "New South Wales"))

@@

```{r basic-manip, out.width="100%", out.height="70%", fig.cap="A glyph map of the average maximum temperature by month of Victoria and New South Wales weather stations in Australia. On the top left corner is an insetted plot of station Cobar highlighted in the black box."}
knitr::include_graphics("figures/basic-manip.png")
```

>>>>

```{r eval = FALSE, echo = TRUE}
tmax <- weatherdata::historical_tmax |>
  filter(between(stringr::str_sub(id, 7, 8), 46, 90))
```

@@

```{r eval=  FALSE, echo = TRUE}
tmax <- tmax |> 
  face_temporal() |>
  filter(lubridate::year(date) %in% c(1971:1975, 2016:2020)) 
```

@@

```{r eval=  FALSE, echo = TRUE}
tmax <- tmax |>
  group_by(month = lubridate::month(date), 
         group = as.factor(ifelse(lubridate::year(date) > 2015, 
                                  "2016 ~ 2020", "1971 ~ 1975"))) |>
  summarise(tmax = mean(tmax, na.rm = TRUE))
```

@@

```{r eval = FALSE, echo = TRUE}
tmax <- tmax |> face_spatial() |> filter(nrow(ts) == 24) 
```

@@

```{r eval = FALSE, echo = TRUE}  
tmax <- tmax |> face_temporal() |> unfold(latitude, longitude)
```

@@

```{r eval = FALSE, echo = TRUE}
nsw_vic <- ozmaps::abs_ste |> 
  filter(NAME %in% c("Victoria", "New South Wales"))

@@

```{r basic-manip, out.width="100%", out.height="70%", fig.cap="A glyph map of the average maximum temperature by month of Victoria and New South Wales weather stations in Australia. On the top left corner is an insetted plot of station Cobar highlighted in the black box."}
knitr::include_graphics(here::here("figures/basic-manip.png"))
```

### 2022-04-17 4-2-agg.Rmd
%>% to |>

```{r echo = TRUE, eval = FALSE}
station_nested <- weatherdata::climate_full %>% 
  mutate(cluster = ...)
```

@@

```{r echo = TRUE}
cluster_nested <- station_nested %>% switch_key(cluster) 
```

@@

```{r eval = FALSE, echo = TRUE}
cluster_nested <- cluster_nested %>% get_centroid()
```

@@

```{r basic-agg, out.width="100%", fig.cap="Profile of aggregated precipitation from 639 weather stations in Australia. Subplot A shows the glyph map of the weekly averaged precipitation of each cluster. The group number of printed in the middle of y minor axis and can be used as a reference line to read the magnitude. Subplot B shows the station membership of each cluster."}
knitr::include_graphics("figures/basic-agg.png")
```

>>>>

```{r echo = TRUE, eval = FALSE}
station_nested <- weatherdata::climate_full |> 
  mutate(cluster = ...)
```

@@

```{r echo = TRUE}
cluster_nested <- station_nested |> switch_key(cluster) 
```

@@

```{r eval = FALSE, echo = TRUE}
cluster_nested <- cluster_nested |> get_centroid()
```

@@

```{r basic-agg, out.width="100%", fig.cap="Profile of aggregated precipitation from 639 weather stations in Australia. Subplot A shows the glyph map of the weekly averaged precipitation of each cluster. The group number of printed in the middle of y minor axis and can be used as a reference line to read the magnitude. Subplot B shows the station membership of each cluster."}
knitr::include_graphics(here::here("figures/basic-agg.png"))
```

### 2022-04-17 4-3-water-level.Rmd
%>% to |>

```{r}
climate <- weatherdata::climate_full %>%
  filter(between(stringr::str_sub(id, 7, 8), 76, 90)) %>%
  stretch() %>%
  filter(lubridate::year(date) == 2020) %>%
  tamp() %>%
  mutate(type = "climate")

river <- weatherdata::water %>%
  mutate(type = "river")
```

```{r matching-map, out.width="100%", fig.cap="Location of weather stations and river gauges in Victoria, Australia."}
knitr::include_graphics("figures/matching-map.png")
```

@@

```{r}
res %>% print(n = 8)
```

@@

```{r matching, out.width="100%", fig.cap="Matched weather stations and river gauges on the map (A) and across time (B). Precipitation and water level have been standardised between 0 and 1 to be displayed on the same scale. The increases in the precipitation is reflected by the water level."}
knitr::include_graphics("figures/matching.png")
```

>>>>

```{r}
climate <- weatherdata::climate_full |>
  filter(between(stringr::str_sub(id, 7, 8), 76, 90)) |>
  face_temporal() |>
  filter(lubridate::year(date) == 2020) |>
  face_spatial() |>
  mutate(type = "climate")

river <- river |> mutate(type = "river")
```

```{r matching-map, out.width="100%", fig.cap="Location of weather stations and river gauges in Victoria, Australia."}
knitr::include_graphics(here::here("figures/matching-map.png"))
```

@@

```{r}
res |> print(n = 8)
```

@@

```{r matching, out.width="100%", fig.cap="Matched weather stations and river gauges on the map (A) and across time (B). Precipitation and water level have been standardised between 0 and 1 to be displayed on the same scale. The increases in the precipitation is reflected by the water level."}
knitr::include_graphics(here::here("figures/matching.png"))
```

### 2022-04-17 4-5-interactive.Rmd
%>% to |>

```{r eval = FALSE, echo = TRUE}
# data pre-processing
clean <- weatherdata::climate_full %>% ...

# created SharedData instance for crosstalk
nested <- clean %>% SharedData$new(~id, group = "cubble")
long <- stretch(clean) %>% SharedData$new(~id, group = "cubble")

# create the spatial and temporal view each with a ShareData instance
p1 <- nested %>% ...
p2 <- long %>% ...

@@

```{r eval = FALSE, echo = TRUE}
# data pre-processing
clean <- weatherdata::climate_full %>% ...

# use the long form to create subplots for each station
df_id <- unique(clean$id)
p <- map(1:length(df_id), function(i){
  dt <- clean %>% filter(id == df_id[i])
  ggplot(dt) %>% ...
})

# create nested form leaflet map with temperature band as subplots 
nested <- tamp(clean)
leaflet(nested) %>% 
  addTiles() %>% 
  addCircleMarkers(group = "a", ...) %>% 
  leafpop::addPopupGraphs(graph = p, ...)

>>>>

``` r
# data pre-processing
clean <- weatherdata::climate_full |> ...

# created SharedData instance for crosstalk
nested <- clean |> SharedData$new(~id, group = "cubble")
long <- face_temporal(clean) |> SharedData$new(~id, group = "cubble")

# create the spatial and temporal view each with a ShareData instance
p1 <- nested |> ...
p2 <- long |> ...

@@

``` r
# data pre-processing
clean <- weatherdata::climate_full |> ...

# use the long form to create subplots for each station
df_id <- unique(clean$id)
p <- map(1:length(df_id), function(i){
  dt <- clean |> filter(id == df_id[i])
  ggplot(dt) |> ...
})

# create nested form leaflet map with temperature band as subplots
nested <- face_spatial(clean)
leaflet(nested) |>
  addTiles() |>
  addCircleMarkers(group = "a", ...) |>
  leafpop::addPopupGraphs(graph = p, ...)
